\sysfull

### 2018-04-16 paper/evaluation.tex
Working on evaluation text

@@

Another critical observation is that \textbf{fft} benchmark did not complete at any distance larger than 0.15\,cm. As we will show now, \sys tast downscaling mechanism will be able to solve this issue.

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/coala_alpaca_gcc}
	\caption{Performance of \sys applications at multiple WISP to RF generator antenna distances \{0.15, 0.3, 0.5\}\,m (left, center and right-most bar per application, respectively), compared against Alpaca (results normalized). Results show that \sys performs on average better than Alpaca for majority of the benchmarks. For specific benchmarks \sys performs worse than Alpaca \todo{state why it is sometimes worse}{Przemek}}
	\label{fig:runtime}
\end{figure}

\textbf{Task Downscaling.} The result is presented in Figure~\ref{fig:task_downscaling} \todo{Provide text; add results}{Przemek}

\begin{figure}
	\centering
	\caption{Task downscaling performance. \todo{Generate taks downscaling figure}{Carlo, Amajda}}
	\label{fig:task_downscaling}
\end{figure}

>>>>

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/coala_alpaca_gcc}
	\caption{Performance of \sys applications at multiple WISP to RF generator antenna distances \{0.15, 0.3, 0.5\}\,m (left, center and right-most bar per application, respectively), compared against Alpaca (results normalized) for ETA coalescing strategy. Results show that \sys performs on average better than Alpaca for majority of the benchmarks. For specific benchmarks \sys performs worse than Alpaca \todo{state why it is sometimes worse}{Carlo}}
	\label{fig:runtime}
\end{figure}

@@

Another critical observation is that \textbf{fft} benchmark did not complete at any distance larger than 0.15\,cm. As we will show now, \sys task downscaling mechanism will be able to solve this issue.

\textbf{Task Downscaling Execution Time.} We have enabled task downscaling and measured the execution time for \textbf{fft} benchmark at all distances that this benchmark could not execute (refer again to Figure~\ref{fig:coalescing} and $\infty$ marks). \sys could execute the benchmark successfully with the execution time of X, Y and Z for distances $d=\{0.3, 0.5. 0.6\}$\,cm, respectively.
